The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-18 Background/impact.tex
fixed bibtex entries for phishing, spoofing

\begin{itemize}
	\item Phishing and Spoofing Attacks\\
    Phishing~\cite{wiki:Phishing} (a variation of spoofing~\cite{wiki:Spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one. The e-mail usually redirects them to a malicious website, which then steals their credentials.

>>>>

\begin{itemize}
	\item Phishing and Spoofing Attacks\\
    Phishing~\cite{phishing} (a variation of spoofing~\cite{spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one. The e-mail usually redirects them to a malicious website, which then steals their credentials.
